Drake Plan

### 2019-08-29 R/drake_plan_conus.Rmd
fix the issue that cv will always rerun itself, use hard copy

```{r}
# drake plan to run cv and output results 
conus_plan_cv <- drake_plan(
  # 5. CV -----------------------------------------------------------
  new_var = target(read_new_var(sat), transform = map(sat = !!sats)),
  cv_results = target(run_cv(dt = new_var), transform = map(new_var, .id = sat)),

@@

```{r, eval = F}
# make(conus_plan, cache = ssd_cache)

time0 <- Sys.time()
future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(conus_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20)
Sys.time() - time0

make(conus_plan_cv, cache = ssd_cache)

>>>>

```{r}
source(here("R/drake_funcs.R"))
# drake plan to run cv and output results 
conus_plan_cv <- drake_plan(
  # 5. CV -----------------------------------------------------------
  new_var = target(read_new_var(sat), transform = map(sat = !!sats)),
  new_dt = target(prepare_dt(new_var), transform = map(new_var, .id = FALSE)),
  cv_results = target(run_cv(dt = new_dt), transform = map(new_dt, .id = sat)),

@@

```{r, eval = F}
# make(conus_plan, cache = ssd_cache)
time0 <- Sys.time()
future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(conus_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20)
Sys.time() - time0

# Allowing `add_hist` in `plot_scatter` (or use plotly) requires set lock_envir to FALSE:
make(conus_plan_cv, cache = ssd_cache, lock_envir = FALSE)
